---
title: 'Examples of using GraphMM package'
author: 'Tien Vo, Michael Newton'
date: '`r format(Sys.time(), '%d %B, %Y')`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Examples of using GraphMM package}
  %\VignetteEngine{knitr::rmarkdown}
    \usepackage[utf8](inputenc)
---

Loading library
```{r loadlib}
library(GraphMM)
```


### Example with data of type vector

Simulate data from multivariate normal distribution

```{r simulatedata}
set.seed(12345)
n.ver = 20
m1 = 100
m2 = 150 
dat1.vec = MASS::mvrnorm(n=m1, mu=c(rep(0, n.ver/2),rep(0.4, n.ver/2)), Sigma = diag(0.5, n.ver, n.ver))
dat2.vec = MASS::mvrnorm(n=m2, mu=c(rep(0, n.ver/2), rep(0.6, n.ver/2)), Sigma = diag(0.7, n.ver, n.ver))

dataG1 = dat1.vec
dataG2 = dat2.vec

```
Use function GraphMMcompute() to perform multiple hypothesis testing for equal means. Since the method is computationally heavy, it is suggested to use 8 cores to run this example.

```{r analysis}
mccores = 8
res = GraphMMcompute(dataG1, dataG2, mccores = mccores)
print(res)
```

### Example with data of type matrix

Simulate data from multivariate normal distribution

```{r simulatedata2}
set.seed(4779541)
datadim = c(3,3)
n.ver = prod(datadim)
m1 = 200
m2 = 250 
dat1.vec = MASS::mvrnorm(n=m1, mu=c(1, 1, 1, 1, 1, 0, 0, 2, 2), 
                         Sigma = diag(0.7, n.ver, n.ver))
dat2.vec = MASS::mvrnorm(n=m2, mu=c(1.2, 1.2, 1.2, 1.2, 1.2, 0, 0, 2, 2), 
                         Sigma = diag(1, n.ver, n.ver))

dataG1 = array(c(dat1.vec), c(m1, datadim))
dataG2 = array(c(dat2.vec), c(m2, datadim))

```
Use function GraphMMcompute() to perform multiple hypothesis testing for equal means. Since the method is computationally heavy, it is suggested to use 8 cores to run this example.

```{r analysis2}
folder="./Temp"
est_null = "ashr"
est_hyper = "mixed"
mccores = 8

res = GraphMMcompute(dataG1 = dataG1, dataG2 = dataG2,
                       est_null = est_null, est_hyper = est_hyper, 
                       folder = folder, mccores = mccores)
print(res)
```
